Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-12-27 ms.qmd
Added details on simulation justification

We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats. The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed. To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:

>>>>

Changes in $lnVR_{Q_{10}}$ are expected to depend on differences in the among-individual variation in the thermal performance curves across species [@angilletta2009thermal]. In other words, we expect performance curves to vary among individuals within a population and this variation is expected to co-vary with habitats [@angilletta2009thermal]. To understand how differences in thermal performance curve variation correlate with the empirical patterns of variance change we observe, we conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats. The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed. To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
